An Exposition on the Propriety of Restricted Boltzmann Machines

### 2016-07-28 presentations/jsm2016/index.Rmd
update bitly

---
title: "An Exposition on the Propriety of Restricted Boltzmann Machines"
author: http://bit.ly/jsm2016
ratio: 16x10
output:
  rmdshower::shower_presentation:
    self_contained: false
    theme: ribbon
    katex: true
    fig_caption: true
    css: style.css
bibliography: refs.bib
---

@@

<p class="white">
Andee Kaplan, Daniel Nordman, and Stephen Vardeman<br/>
Iowa State University<br/>
July 31, 2016<br/>
JSM - Chicago, IL<br/>
</br></br></br></br>
<a href="http://bit.ly/jsm2016">http://bit.ly/jsm2016</a>
</p>

>>>>

---
title: "An Exposition on the Propriety of Restricted Boltzmann Machines"
author: http://bit.ly/jsm2016-rbm
ratio: 16x10
output:
  rmdshower::shower_presentation:
    self_contained: false
    theme: ribbon
    katex: true
    fig_caption: true
    css: style.css
bibliography: refs.bib
---

@@

<p class="white">
Andee Kaplan, Daniel Nordman, and Stephen Vardeman<br/>
Iowa State University<br/>
July 31, 2016<br/>
JSM - Chicago, IL<br/>
</br></br></br></br>
<a href="http://bit.ly/jsm2016-rbm">http://bit.ly/jsm2016-rbm</a>
</p>
